\LARGE \bf Geometric Adaptive Control of Attitude Dynamics on $\SO$\\ with State Inequality Constraints

### 2015-09-21 ACC16.2.tex
start of error dynamics proposition

Discussion of error function

Give some bounds on B?

The attractive error function has been used for attitude control on \SO.
In order to incorporate the state inequality constraints we apply the logarithmic barrier function.
The positive constant \( \alpha \) serves to shape the barrier function.
As \( \alpha \) is increased the impact of \( B(R) \) is reduced.

\Cref{eqn:psi} is composed of an attractive term \( A (R) \) and a repulsive term \( B(R) \) which are given by
Here we summarize

Log barrier for repulsive term
Some properties of the log barrier term

Standard attractive error function
Configuration error function with attractive and repulsive terms
Define the various attitude error functions and where they are derived from
summarize some of the properties of the attractive error function from previous papers

Show the development of the configuration error terms and equilibrium structure

Derive error dynamics

@@

\begin{prop}[Error Dynamics]\label{prop:error_dyn}
Error dynamics (time derivatives of everything)
\end{prop}
\begin{proof}
	Either here or in the appendix
\end{proof}

@@

\subsection{Proof of }
Detail on finding bounds of \( \norm{\dot{e}_R} \)

>>>>

\Cref{eqn:psi} is composed of an attractive term \( A (R) \) and a repulsive term \( B(R) \).
The attractive error function has been used for attitude control on \SO.
In order to incorporate the state inequality constraints we apply a logarithmic barrier function term.
Barrier functions are typically used in optimal control and motion planning applications.
As the boundary of the constraint is neared, or \( r^T R^T v \to \cos \theta \), the barrier term increases, \( B \to \infty\).
The logarithmic function is popular as it quickly decays away from the constraint boundary.
The positive constant \( \alpha \) serves to shape the barrier function.
As \( \alpha \) is increased the impact of \( B(R) \) is reduced away from the constraint boundary.

\begin{prop}[Error Dynamics]\label{prop:error_dyn}
	The attitude error dynamics for \( \Psi, e_R, e_\Omega \) satisfy

	Psi dot

	er dot

	er B dot

	erA dot

	A dot

	B dot

	e omega dot

\end{prop}

\begin{proof}
	See~\Cref{proof:error_dyn}
\end{proof}

@@

@@

\subsection{Proof of~\Cref{prop:error_dyn}}\label{proof:error_dyn}

Detail on finding bounds of \( \norm{\dot{e}_R} \)
